Contextuality and the Born rule in fuzzy quantum theories

### 2017-03-25 prop_letter.tex
prop_letter.tex \allowdisplaybreaks Added...
prop_letter.tex Updating here and there...

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\linewidth}\color{green}{Amr says: #1}\end{minipage}}}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\linewidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}
\def\C{{\mathbb{C}}}
\newcommand{\Tr}{\mathop{\mathrm{Tr}}\nolimits}

@@

Assume there is a function~$v:\events_{24}\rightarrow\left\{ 0,1\right\} $
satisfying equation~(\ref{eq:Kochen-Specker-Rules}). There must
be a quantum IVPM~$\bar{\mu}_{24}:\events_{24}\rightarrow\mathscr{I}_{\mathrm{D}}$
defined by $\bar{\mu}_{24}\left(P\right)=\iota_{\mathrm{D}}\left(v\left(P\right)\right)$,
where 
\begin{equation}
\iota_{\mathrm{D}}\left(x\right)=\begin{cases}
\necess & \text{, if }x=1\text{ ;}\\
\imposs & \text{, if }x=0\text{ .}
\end{cases}\label{eq:homomorphism-0}
\end{equation}
Hence, there exists an interval-valued frame function~$\bar{f}:\mathcal{T}_{24}\rightarrow\mathscr{I}_{\mathrm{D}}$
defined by $\bar{f}\left(\ket{\psi}\right)=\bar{\mu}_{24}\left(\proj{\psi}\right)$
satisfying the following conditions because the right-hand side of
each equation forms an orthogonal basis and we can apply Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})\begin{subequations}\label{eq:Kernaghan}
\begin{eqnarray}
\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,1,0,0)\nonumber \\*
 &  & +\bar{f}(0,0,1,0)+\bar{f}(0,0,0,1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,1,0,0)\nonumber \\
 &  & +\bar{f}(0,0,1,1)+\bar{f}(0,0,1,-1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,0,1,0)\nonumber \\*
 &  & +\bar{f}(0,1,0,1)+\bar{f}(0,1,0,-1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,0,0,1)\nonumber \\*
 &  & +\bar{f}(0,1,1,0)+\bar{f}(0,1,-1,0)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(-1,1,1,1)+\bar{f}(1,-1,1,1)\nonumber \\
 &  & +\bar{f}(1,1,-1,1)+\bar{f}(1,1,1,-1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(-1,1,1,1)+\bar{f}(1,1,-1,1)\nonumber \\*
 &  & +\bar{f}(1,0,1,0)+\bar{f}(0,1,0,-1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(-1,1,1,1)+\bar{f}(1,1,-1,1)\nonumber \\*
 &  & +\bar{f}(0,1,1,0)+\bar{f}(1,0,0,-1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(1,1,-1,1)+\bar{f}(1,1,1,-1)\nonumber \\*
 &  & +\bar{f}(0,0,1,1)+\bar{f}(1,-1,0,0)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(0,1,-1,0)+\bar{f}(1,0,0,-1)\nonumber \\*
 &  & +\bar{f}(1,1,1,1)+\bar{f}(1,-1,-1,1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(0,0,1,-1)+\bar{f}(1,-1,0,0)\nonumber \\*
 &  & +\bar{f}(1,1,1,1)+\bar{f}(1,1,-1,-1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(1,0,1,0)+\bar{f}(0,1,0,1)\nonumber \\*
 &  & +\bar{f}(1,1,-1,-1)+\bar{f}(1,-1,-1,1)\textrm{ .}
\end{eqnarray}
\end{subequations}If we sum up equation~\ref{eq:Kernaghan}, we
will have
\begin{eqnarray}
\left[11,11\right] & \subseteq & 4\bar{f}(1,0,0,0)+4\bar{f}(-1,1,1,1)\nonumber \\
 &  & +2\sum_{\ket{\psi}\in\mathcal{T}_{18}}\bar{f}\left(\ket{\psi}\right)\textrm{ ,}\label{eq:QuantumInterval-valuedProbability-Total}
\end{eqnarray}
where 
\begin{eqnarray}
\mathcal{T}_{18} & = & \mathcal{T}_{24}\backslash\{(1,0,0,0),(-1,1,1,1),(1,-1,1,-1),\nonumber \\
 &  & (1,0,-1,0),(1,0,0,1),(1,1,0,0)\}\textrm{ .}
\end{eqnarray}
However, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Total})
can never be satisfied. Because each term in left-hand side is either
$\imposs=\left[0,0\right]$ or $\necess=\left[1,1\right]$, the left-hand
side is a singleton set of an even integer while the right-hand side
is $\left\{ 11\right\} $. Therefore, there is no quantum IVPM~$\bar{\mu}_{24}:\events_{24}\rightarrow\mathscr{I}_{\mathrm{D}}$.
Moreover, there is no quantum IVPM defined on the set of all projectors
as well; otherwise, if we have a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$,
then we can restrict $\bar{\mu}$ and define $\bar{\mu}_{24}=\left.\bar{\mu}\right|_{\events_{24}}$.

@@

Recall we model the idea of the finite precision measurement as IVPM.
Given a quantum IVPM, the natural question would be whether we are
able to refine precisely enough to determine the underlying unknown
quantum real-valued probability measure, i.e., a quantum state. This
leads to the definition of core:\begin{definition}A \emph{core} of
$\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\set{\pmeas:\events\rightarrow[0,1]}{\forall P\in\events.~\pmeas\left(P\right)\in\bar{\mu}\left(P\right)}$.\end{definition}For
example, we can add an one extra interval~$\unknown=\left[0,1\right]$
to $\mathscr{I}_{\mathrm{D}}$, and consider $\mathscr{I}_{1}=\left\{ \imposs,\unknown,\necess\right\} $.
Let 
\begin{equation}
\iota_{1}(x)=\begin{cases}
\necess & \text{ if}x=1\text{ ;}\\
\imposs & \text{ if}x=0\text{ ;}\\
\unknown & \text{ otherwise.}
\end{cases}\label{eq:homomorphism-1}
\end{equation}
Then, $\iota_{1}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}:\events\rightarrow\mathscr{I}_{1}$
is a quantum IVPM, and we have $\mathrm{core}\left(\iota_{1}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right)=\left\{ \mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right\} $,
where $\circ$ denote function composition.

While Shapley proved a good enough classical IVPM always has a non-empty
core, and we haven't found any classical IVPM having an empty core,
there are some simple quantum IVPM which has an empty core.

\begin{thm}[Shapley~\citep{Shapley1971,Grabisch2016}]\label{thm:Shapley}
Every classical convex interval-valued probability measure has a non-empty
core, where $\bar{\mu}$ is called convex if 
\begin{equation}
\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\label{eq:QuantumInterval-valuedProbability-Convex}
\end{equation}
for all commuting $P_{0},P_{1}\in\events$, and the \emph{disjunction}~$P_{0}\vee P_{1}$
is defined to be $P_{0}+P_{1}-P_{0}P_{1}$~\citep{Griffiths2003}.\end{thm}

@@

>>>>

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\linewidth}\color{green}{Amr says: #1}\end{minipage}}}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\linewidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}
\def\C{{\mathbb{C}}}
\newcommand{\Tr}{\mathop{\mathrm{Tr}}\nolimits}
\allowdisplaybreaks

@@

Assume there is a function~$v:\events_{24}\rightarrow\left\{ 0,1\right\} $
satisfying equation~(\ref{eq:Kochen-Specker-Rules}). There must
be a quantum IVPM~$\bar{\mu}_{24}:\events_{24}\rightarrow\mathscr{I}_{\mathrm{D}}$
defined by $\bar{\mu}_{24}\left(P\right)=\iota_{\mathrm{D}}\left(v\left(P\right)\right)$,
where 
\begin{equation}
\iota_{\mathrm{D}}\left(x\right)=\begin{cases}
\necess & \text{, if }x=1\text{ ;}\\
\imposs & \text{, if }x=0\text{ .}
\end{cases}\label{eq:homomorphism-0}
\end{equation}
Hence, there exists an interval-valued frame function~$\bar{f}:\mathcal{T}_{24}\rightarrow\mathscr{I}_{\mathrm{D}}$
defined by $\bar{f}\left(\ket{\psi}\right)=\bar{\mu}_{24}\left(\proj{\psi}\right)$
satisfying the following conditions because the right-hand side of
each equation forms an orthogonal basis and we can apply Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})\begin{subequations}\label{eq:Kernaghan}
\begin{eqnarray}
\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,1,0,0)\nonumber \\*
 &  & +\bar{f}(0,0,1,0)+\bar{f}(0,0,0,1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,1,0,0)\nonumber \\*
 &  & +\bar{f}(0,0,1,1)+\bar{f}(0,0,1,-1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,0,1,0)\nonumber \\*
 &  & +\bar{f}(0,1,0,1)+\bar{f}(0,1,0,-1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,0,0,1)\nonumber \\*
 &  & +\bar{f}(0,1,1,0)+\bar{f}(0,1,-1,0)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(-1,1,1,1)+\bar{f}(1,-1,1,1)\nonumber \\*
 &  & +\bar{f}(1,1,-1,1)+\bar{f}(1,1,1,-1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(-1,1,1,1)+\bar{f}(1,1,-1,1)\nonumber \\*
 &  & +\bar{f}(1,0,1,0)+\bar{f}(0,1,0,-1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(1,-1,1,1)+\bar{f}(1,1,-1,1)\nonumber \\*
 &  & +\bar{f}(0,1,1,0)+\bar{f}(1,0,0,-1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(1,1,-1,1)+\bar{f}(1,1,1,-1)\nonumber \\*
 &  & +\bar{f}(0,0,1,1)+\bar{f}(1,-1,0,0)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(0,1,-1,0)+\bar{f}(1,0,0,-1)\nonumber \\*
 &  & +\bar{f}(1,1,1,1)+\bar{f}(1,-1,-1,1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(0,0,1,-1)+\bar{f}(1,-1,0,0)\nonumber \\*
 &  & +\bar{f}(1,1,1,1)+\bar{f}(1,1,-1,-1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(1,0,1,0)+\bar{f}(0,1,0,1)\nonumber \\*
 &  & +\bar{f}(1,1,-1,-1)+\bar{f}(1,-1,-1,1)\textrm{ .}
\end{eqnarray}
\end{subequations}If we sum up Eq.~(\ref{eq:Kernaghan}), we will
have
\begin{eqnarray}
\left[11,11\right] & \subseteq & 4\bar{f}(1,0,0,0)+4\bar{f}(1,1,-1,1)\nonumber \\
 &  & +2\sum_{\ket{\psi}\in\mathcal{T}_{18}}\bar{f}\left(\ket{\psi}\right)\textrm{ ,}\label{eq:QuantumInterval-valuedProbability-Total}
\end{eqnarray}
where 
\begin{eqnarray}
\mathcal{T}_{18} & = & \mathcal{T}_{24}\backslash\{(1,0,0,0),(1,1,-1,1),(1,-1,1,-1),\nonumber \\
 &  & (1,0,-1,0),(1,0,0,1),(1,1,0,0)\}\textrm{ .}
\end{eqnarray}
However, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Total})
can never be satisfied. Because each term in right-hand side is either
$\imposs=\left[0,0\right]$ or $\necess=\left[1,1\right]$, the right-hand
side is a singleton set of an even integer while the left-hand side
is $\left\{ 11\right\} $. Therefore, there is no quantum IVPM~$\bar{\mu}_{24}:\events_{24}\rightarrow\mathscr{I}_{\mathrm{D}}$.
Moreover, there is no quantum IVPM defined on the set of all projectors
as well; otherwise, if we have a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$,
then we can restrict $\bar{\mu}$ and define $\bar{\mu}_{24}=\left.\bar{\mu}\right|_{\events_{24}}$.

@@

Recall we model the idea of the finite precision measurement as IVPM.
When we made finite number of observations, we can use some quantum
IVPMs to represent what we observed. The natural question would be
whether we are able to refine precisely enough to determine the underlying
unknown quantum real-valued probability measure, i.e., a quantum state.
This leads to the definition of core:\begin{definition}A \emph{core}
of $\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\set{\pmeas:\events\rightarrow[0,1]}{\forall P\in\events.~\pmeas\left(P\right)\in\bar{\mu}\left(P\right)}$.\end{definition}For
example, we can add an one extra interval~$\unknown=\left[0,1\right]$
to $\mathscr{I}_{\mathrm{D}}$, and consider $\mathscr{I}_{1}=\left\{ \imposs,\unknown,\necess\right\} $.
Let 
\begin{equation}
\iota_{1}(x)=\begin{cases}
\necess & \text{, if }x=1\text{ ;}\\
\imposs & \text{, if }x=0\text{ ;}\\
\unknown & \text{, otherwise.}
\end{cases}\label{eq:homomorphism-1}
\end{equation}
Then, $\iota_{1}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}:\events\rightarrow\mathscr{I}_{1}$
is a quantum IVPM whose core has a unique element~$\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}$,
where $\circ$ denote function composition.

However, not every quantum IVPM well represent our observations. The
following example provides a quantum IVPM with an empty core, i.e.,
it cannot be further refined to get the underlying unknown quantum
states.

@@

While the above example alerts that there might be a bad choice to
represent our observations as a quantum IVPM, this phenomena is quantum,
because Shapley proved that a good enough classical IVPM always has
a non-empty core. \begin{thm}[Shapley~\citep{Shapley1971,Grabisch2016}]\label{thm:Shapley}Every
classical convex interval-valued probability measure has a non-empty
core, where $\bar{\mu}$ is called convex if 
\begin{equation}
\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\label{eq:QuantumInterval-valuedProbability-Convex}
\end{equation}
for all commuting $P_{0},P_{1}\in\events$, and the \emph{disjunction}~$P_{0}\vee P_{1}$
is defined to be $P_{0}+P_{1}-P_{0}P_{1}$~\citep{Griffiths2003}.\end{thm}
In general, we haven't found any classical IVPM having an empty core.
